\documentclass[]{friggeri-cv}
\usepackage{graphicx}
\usepackage{eurosym}

\begin{document}

\header{Stefano}{Munarini}{Software Developer}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside}
\section{contacts}
% Jämeräntaival 6 B 207
% Otaniemi, Espoo, 02150
+358 (0) 46 9424916
\href{mailto:stefano.munarini@me.com}{stefano.munarini@me.com}
% \textbf{Skype}:
% stefano.munarini
% \section{accounts}
\href{https://it.linkedin.com/in/munarinistefano}{\textbf{LinkedIn}:
munarinistefano}
\href{https://github.com/stefanomunarini}{\textbf{GitHub}:
munarinistefano}
\href{http://stackexchange.com/users/2741833/stefano-munarini}{\textbf{StackOverflow}:
2741833}
\section{skills}
Teamwork, Prototyping,
Architecture Design,
Python, Javascript,
Docker, Git
% Java, SQL
% , SQL, HTML, 
\section{languages}
Italian mother tongue
English proficient
\section{certifications}
IELTS Bandscore 7
\section{awards}
\href{http://www.wired.it/mobile/app/2013/12/17/upperapp-migliori-app-studenti/}{"Best Mobile App Developed by Students" UpperApp(2013)}
\href{https://devpost.com/software/donatewise}{"Moving Money Without Borders" Transferwise(2016)}
\end{aside}

%----------------------------------------------------------------------------------------
%	ABOUT ME SECTION
%----------------------------------------------------------------------------------------

\section{about me}
{
A passionate and well-rounded developer, with an high capacity of problem solving, who is able to convert complex problems into smaller and easier tasks. A good team player but also a team leader if needed, who is able to listen and to compare ideas with others to drive teams to better solutions. \\
% A good background in web development with Python, Django, JavaScript, MySQL, PostgreSQL, Docker, Cron and Git achieved during his work experience in London, starting as an intern in a startup called TutorCruncher and continued as Python Developer at Tangent Snowball, a digital agency responsible for developing projects for clients such as PepsiCo, Sky, Carlsberg, Wolseley and many more. \\
% A good background in Android development confirmed by the popularity (over 90k downloads) and the rating (4.5/5) of his application “Libretto Universitario" in the Google Play Store, and certified by the winning of the first price as “Best mobile application of 2013” at the UpperApp festival. A good academic background in web development with Java technologies, as well as with the Spring framework.
% \\
A natural explorer and a traveler who had met lots of different cultures that enabled him to open his mind while teaching him values such as respect, adaptability and integrity.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

{Feb 2016 -- Jul 2016} \\
{\textbf{Python Developer}} \\
{\href{http://www.tangentsnowball.com}{Tangent Snowball}} -- {London, UK} \\
{This role encompassed the development of CRM platforms, APIs and microservices. My responsabilities were to design and implement the services, while also collaborate with the data team to normalize and automate the data collection process.
I was also responsible for the development of a set of APIs aimed at porting some of the functionalities of the Counts for More platform (PepsiCo) to a mobile application.
The technology stack was made of Python, Django, JavaScript, HTML, MySQL, PostgreSQL, Docker and Git.}

{Jan 2016 -- Feb 2016} \\
{\textbf{Python Developer}} \\
{\href{http://www.tutorcruncher.com}{TutorCruncher}} -- {London, UK} \\
{Responsible for developing functionalities of TutorCruncher, a cloud-based platform developed in Django.}

{Feb 2014 -- Jun 2014} \\
{\textbf{Android Developer}} \\
{\href{http://www.dedagroup.it}{Dedagroup ICT Network}} -- {Trento, Italy} \\
{This role encompassed the design and development of an Android application aimed at helping people affected by Alzheimer's Disease. The role encompassed all aspects of software design, both fronted and backend, including architectural decisions.
The technology stack was made of Java, Spring, Android, MySQL and Git.}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{projects}

{Sep 2013 - Present} \\
{\textbf{Libretto Universitario}} \\
Libretto Universitario is an Android application which aims at easying the management of every university-related aspects of all Italian students. The application has been downloaded 100k times in less than 2 years.
% , with revenue of over 10k \euro.


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

% \section{awards}

% {Dec 2013} \\
% {\textbf{\href{http://www.upperapp.it}{UpperApp Festival} - 1\textsuperscript{st} Prize: Best Mobile Application of 2013} \\
% {Agorà Telematica} \\
% Libretto Universitario has been awarded as \textit{Best Mobile Application} of 2013 at the UpperApp Festival.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

{2016 -- 2017} \\
\textbf{Masters Degree {\normalfont in Software and Service Architectures}} \\
{Aalto University, Finland} \\

{2011 -- 2015} \\
\textbf{Bachelor Degree {\normalfont in Computer Science}} \\
{University of Trento, Italy}

\end{document}